---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rYoctoPuceInOut

<!-- badges: start -->
[![R Universe version](https://aphalo.r-universe.dev/badges/rYoctoPuceInOut)](https://aphalo.r-universe.dev/rYoctoPuceInOut)
[![R-CMD-check](https://github.com/aphalo/rYoctoPuceInOut/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/aphalo/rYoctoPuceInOut/actions/workflows/R-CMD-check.yaml)
[![Documentation](https://img.shields.io/badge/documentation-rYoctoPuceInOut-informational.svg)](https://docs.r4photobiology.info/rYoctoPuceInOut/)
<!-- badges: end -->

## Warning

Package 'rYoctoPuceInOut' is at a very early stage of development. Function
interfaces and object names are still subject to changes likely  to
break code written for the current version 'rYoctoPuceInOut' (== `r packageVersion('rYoctoPuceInOut')`).

## Purpose

The goal of 'rYoctoPuceInOut' is to facilitate the import of data saved by
the built-in logger of various USB modules made by 
[YoctoPuce](https://www.yoctopuce.com/). File import 
functions as well as auxiliary functions that easy the use of the logged data
by applicaton of calibrations are provided, or conversion into objects 
following the expectations of the **R for Photobiology** suite of R packages.

The package includes CSV files with data logged by a selection of different USB
USB modules from *YoctoPuce*. It also includes JSON files with settings for
the same modules.

Package 'rYoctoPuceInOut' is an extension of the R for photobiology suite of
R packages.

## Installation

Package 'rYoctoPuceInOut' is not yet published through CRAN. Currently, it is
easiest to install it from R-Universe. It is also possible to directly install
it from the sources at the GitHUb repository.

In recent versions of R an option can be set to make the author's
repository at R-Universe. Once the option is set installing this package works
similarly as from CRAN.

```{r, eval=FALSE}
repos <- getOption("repos", default = list())
repos[["r4photobiology"]] <- "https://aphalo.r-universe.dev"
options(repos = repos)
```

```{r, eval=FALSE}
install.packages(c('rOmniDriver', 'ooacquire'))
```

Without setting the option, it is also possible to pass the URL of the my
R-Universe repository in the call to `install.packages()`
together with the CRAN URL to ensure that dependencies are installed.

```{r, eval=FALSE}
install.packages(c('rOmniDriver', 'ooacquire'), 
                 repos = c('https://aphalo.r-universe.dev', 
                           'https://cloud.r-project.org'))
```

You can install the same version of 'rYoctoPuceInOut' with:

```{r, eval=FALSE}
remotes::install_github("aphalo/rYoctoPuceInOut")
```

To check the currently installed version use:

```{r}
packageVersion("rYoctoPuceInOut")
```

## Documentation and examples

Documentation includes one vignettes in addition to help pages. The examples in
the vignettes and help pages use example files downloaded from different
YoctoPuce modules. These CSV (data) and JSON (settings) files can be found in
folder `extdata`.

## Examples

This is a basic example which shows you how to solve a common problem:

```{r}
library(rYoctoPuceInOut)

yocto_meteo.file <-
  system.file("extdata", "yocto-meteo-snm.csv",
              package = "rYoctoPuceInOut", mustWork = TRUE)

head(read_yocto_datalog(yocto_meteo.file), 5)
head(read_yocto_datalog(yocto_meteo.file, 
                           cols.pattern = "avg"), 5)
head(read_yocto_datalog(yocto_meteo.file,
                           cols.pattern = "temperature"), 5)
```

```{r}
yocto_spectral.file <-
   system.file("extdata", "yocto-spectral-LED.csv",
             package = "rYoctoPuceInOut", mustWork = TRUE)

head(read_yocto_spctlog(yocto_spectral.file,
                             cols.pattern = "avg"), 5)
```

## Documentation

HTML documentation for this package is available at
(<https://docs.r4photobiology.info/rYoctoPuceInOut/>), including a *User
Guide* and a description of the algorithms.

## Folder Structure

The folder structure of the Git repository is shown below. Folders `.github`, `data-raw` and `articles` are not included in the built package. Folder `data-raw` contains raw data and scripts mostly thought as useful for future use. Folder `tests` contains files implementing unit tests.

```
rYoctoPuceInOut
├── .github 
├── data
├── data-raw
├─┬ inst
│ └── extdata
├── man 
├── R
├─┬ tests
│ └── testthat
└─┬ vignettes
  └── articles
```

## Contributing

Please report bugs and request new features at
(<https://github.com/aphalo/rYoctoPuceInOut/issues>). Pull requests are
welcome at (<https://github.com/aphalo/rYoctoPuceInOut>).

## Citation

If you use 'rYoctoPuceInOut' to produce scientific or commercial publications,
acknowledge this by citing the package according to:

```{r}
citation("rYoctoPuceInOut")
```

## License

© 2025-2026 Pedro J. Aphalo ([pedro.aphalo\@helsinki.fi](mailto:pedro.aphalo@helsinki.fi)). This software carries no warranty of any kind even if carefully designed and coded. The open source code is available for inspection.
