---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rYoctoPuceInOut

<!-- badges: start -->
<!-- badges: end -->

The goal of 'rYoctoPuceInOut' is to facilitate the import of data saved by
the built-in logger of various USB modules made by 
[YoctoPuce](https://www.yoctopuce.com/). File import 
functions as well as auxiliary functions that easy the use of the logged data
are provided. These additional functions currently target the AS7343 digital 
spectral sensor from AMS-Osram used in the *YoctoSpectral* module.

The simulations of channel responses of the AS7343 makes possible *in-silico*
simulations of the retrieval specific quantities of interest such as PAR, ePAR, 
UVA:PAR, R:FR and B:G ratios.

The package includes CSV files with data logged by a selection of different USB
USB modules from *YoctoPuce*.

Package 'rYoctoPuceInOut' is an extension of the R for photobiology suite of
R packages.

## Installation

You can install the development version of 'rYoctoPuceInOut' with:

```{r, eval=FALSE}
remotes::install_github("aphalo/rYoctoPuceInOut")
packageVersion("rYoctoPuceInOut")
```

## Examples

This is a basic example which shows you how to solve a common problem:

```{r example}
library(AS7343)
simul_AS7343(sun.spct, 
             unit.out = "photon",
             scale.factor = 1e-6)
```

```{r}
yocto_meteo.file <-
  system.file("extdata", "yocto-meteo-snm.csv",
              package = "rYoctoPuceInOut", mustWork = TRUE)

head(read_yocto_logger_csv(yocto_meteo.file), 5)
head(read_yocto_logger_csv(yocto_meteo.file, 
                           cols.pattern = "avg"), 5)
head(read_yocto_logger_csv(yocto_meteo.file,
                           cols.pattern = "temperature"), 5)
```

```{r}
yocto_spectral.file <-
   system.file("extdata", "yocto-spectral-LED.csv",
             package = "rYoctoPuceInOut", mustWork = TRUE)

head(read_yocto_spectral_csv(yocto_spectral.file,
                             cols.pattern = "avg"), 5)
```

