---
title: "Plant-Related Quantities"
subtitle: "Package 'rYoctoPuceInOut' `r packageVersion('rYoctoPuceInOut')` "
author: "Pedro J. Aphalo"
date: "`r packageDate('rYoctoPuceInOut')`"
output: 
  html_document:
    toc: yes
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Set up

```{r setup}
library(dplyr)
library(photobiology)
library(photobiologyWavebands)
library(photobiologySensors)
library(photobiologyPlants)
library(photobiologySun)
library(photobiologyLamps)
library(ggspectra)
library(ggpmisc)
library(smatr)
library(rYoctoPuceInOut)
```

```{r}
photon_as_default()
```

## AS7343 spectral response

The AS7343 sensor has 13 channels covering wavelengths in the range 370-900 nm. 

```{r}
ams_AS7343.spct <- sensors.mspct[["ams_AS7343"]]
ams_AS7343.mspct <- subset2mspct(ams_AS7343.spct)
autoplot(ams_AS7343.mspct)
```

The channels correspond to different wavebands. The AS7343's channels can be grouped into eight "narrow-band" channels named in the data sheet as F1 to F8.

```{r}
autoplot(ams_AS7343.mspct[grepl("F[0-9]", 
                                names(ams_AS7343.mspct))])
```

The three channeld FXL, FY, and FZ approximate the red, green and blue sensitivity of the human eye and can be used to describe the colour of light as seen by humans. Alternatively they may work as broader red, green and blue (RGB) channels although the red one has peak sensitivity at around 600 nm.

```{r}
autoplot(ams_AS7343.mspct[grepl("F[XYZ].*", 
                                names(ams_AS7343.mspct))])
```

Finally a broad channel covering the visible (VIS) waveband, although with a broader and more squarish peak shape than corresponding to the standard definition of illuminance. And a rather narrow near infrared channel, most likely included to help detect incandescent lamps and some discharge lamps from LEDs.

```{r}
autoplot(ams_AS7343.mspct[grepl("VIS|NIR", 
                                names(ams_AS7343.mspct))])
```

If we consider the wavelength bands important for plants, VIS matches well ePAR, and F8 perfect for far-red (FR). As the spectral response of the channels is published in the specifications it is possible simulate the response to a known light source spectrum. A couple of functions in packaage 'AS7343' make such simulations easier. In the next section, the response to one terrestrial sunlight spectrum is simulated, explaining the steps.

## A single sunlight spectrum

A single spectrum computed with a radiation transfer model.

```{r}
autoplot(sun.spct, annotations = c("+", "title:where:when:what"))
```

With a list of `waveband` objects we can compute multiple irradiances by integrating the radiation spectrum over multiple ranges of wavelengths. 

```{r}
wavebands <- 
  c(list(PAR("McCree"), PAR("ePAR")),
    Plant_bands("Sellaro"),
    list(Red("Smith20"), Far_red("Smith20")))
```

Compute irradiances

```{r}
irradiances.tb <-
  q_irrad(sun.spct, 
          wavebands, 
          scale.factor = 1e6, # mol m-2 s-1 -> umol m-2 s-1
          return.tb = TRUE)
irradiances.tb
```

The response of the AS7343 sensor can be simulated with a function that convolutes the light spectrum with the respnse spectra for the different channels and intergrates the sensor response accross wavelengths. In `channels.tb` the responses are stored with one row per channel, that is converted into a data frame with one column per channel (`ch.tb`).

```{r}
channels.tb <- 
  simul_sensor_response(sun.spct,
                       sensors.mspct[["ams_AS7343"]],
                       norm = "undo")
ch.tb <- as.data.frame(t(channels.tb[ , -1]))
colnames(ch.tb) <- channels.tb[[1]]
ch.tb
```

By column binding the two data frames that we know contain a single row, a data frame with both irradiances computed from the spectrum and estimates of sensor responses is created.

```{r}
all.data <- cbind(irradiances.tb, ch.tb)
colnames(all.data)
```

The code above produces a row of values for one spectral observation. It
contains data for both the irradiances for different wavebands of interest and
the simulated channel-sensor responses for the AS7343. To find a calibration
recipe that works in sunlight and cloud light, we need to repeat this
computation for a large number of different spectra and fit a model for each
waveband irradiance against the sensor channel responses as explanatory
variables. In principle, multiple linear regression or multiple major axis
regression can be expeted to provide useful calibrations.

To take into account the tolerances of the AS7343 specifications we would need
to replace the deterministic typical response from the data sheet by a
simulation that takes into consideration tolerances. However, guranteed
specifications tend to be much looser than what actual components have,
especially from well known brands as ams OSRAM.

## Multiple sunlight spectra

Multiple spectra computed with a radiation transfer model and available in
R package 'photobiologySun'.

A first calibration attempt in daylight use close to 80 spectra for the latitude of Helsinki simulated through the day course for a few days in June and August. The simulations include the effects of clouds and aerosols in the atmosphere. Using a collection of spectra is easier and faster to we convert the data, The wavelength range ranges up to 800 nm so the NIR channel cannot be included in the analysis.

Currently, a few spectra that are filles with `NA` values have to be removed from the June collection.

```{r}
sun_hourly_june.mspct <- subset2mspct(sun_hourly_june.spct)
sun_hourly_june.mspct <- sun_hourly_june.mspct[1:54] # 55:58 NAs!
unique(wl_min(sun_hourly_june.mspct)$min.wl)
unique(wl_max(sun_hourly_june.mspct)$max.wl)
```

Currently, a few spectra that are filles with `NA` values have to be removed from the August collection.

```{r}
sun_hourly_august.mspct <- subset2mspct(sun_hourly_august.spct)
sun_hourly_august.mspct <- sun_hourly_august.mspct[1:29]
unique(wl_min(sun_hourly_august.mspct)$min.wl)
unique(wl_max(sun_hourly_august.mspct)$max.wl)
```

Data from June and August are concatenated and unique names created.

```{r}
test.mspct <- c(sun_hourly_june.mspct, sun_hourly_august.mspct)
names(test.mspct) <- make.names(names(test.mspct), unique = TRUE)
```

A plot of the spectra shows that they cover a wide range of irradiances.

```{r}
autoplot(test.mspct)
```

Taking advantage of "vectorization" in `q_irrad()` we compute irradiances for all wavebands and spectra in one statement, obtaining a data frame with one row per spectrum.

```{r}
irradiances.tb <-
  q_irrad(test.mspct, 
          wavebands, return.tb = TRUE)
nrow(irradiances.tb)
```

As function `simul_sensor_response()` is not yet vectorised, a `for` loop is needed to "walk" through the spectra in the collection.

```{r}
channels.ls <-list()
spct.names <- names(test.mspct)
AS7343.mspct <- subset2mspct(sensors.mspct[["ams_AS7343"]])
for (name in spct.names) {
#  print(name)
  temp.tb <- simul_sensor_response(test.mspct[[name]][ , 1:2],
                                  AS7343.mspct,
                                  norm = "undo")
  channels.ls[[name]] <- temp.tb[[2]]
}
channels.tb <- as.data.frame(t(as.data.frame(channels.ls)))
colnames(channels.tb) <- temp.tb[["spct.idx"]]
channels.tb[["spct.idx"]] <- spct.names
```

It is safer to join the irradiance and sensor response data matching rows by spectrum name than by position.

```{r}
colnames(irradiances.tb)
colnames(channels.tb)
all_data.tb <- right_join(irradiances.tb, channels.tb)
```

### Simulated calibrations

In principle it would be possible to start with a full models with all 13 channels, or, for example, the eight narrow channels.

```{r, eval = FALSE}
fm1 <- lm(Q_UVA1.CIE ~ F1 + F2 + F3 + F4 + F5 + F6 + F7 + F8, data = all_data.tb)
anova(fm1)
step(fm1)
```

On the other hand, basing the calibrations on individual sensor channels is in practice a lot easier. So, this is worthwhile testing before attempting any more complex model fitting.

### PAR

The first question is: Is the VIS channel a good enough match to be used for PAR measurement in sunlight?

```{r}
ggplot(all_data.tb, aes(Q_PAR.McCree * 1e6, VIS)) +
  geom_point() +
  stat_poly_line(formula = y ~ x + 0, method = "sma") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x + 0, method = "sma")
```

Would it also work for ePAR?

```{r}
ggplot(all_data.tb, aes(Q_ePAR * 1e6, VIS)) +
  geom_point() +
  stat_poly_line(formula = y ~ x + 0, method = "sma") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x + 0, method = "sma")
```

For sunlight the answer to both questions is: yes.

### UVA1

In the case of UVA1, the centre wavelength of the nearest sensor channel is about 20 nm too long. Although $R^2$ remains very high there is more variation around the "calibration" line than for PAR or ePAR.


```{r}
ggplot(all_data.tb, aes(Q_UVA1.CIE, F1)) +
  geom_point() +
  stat_poly_line(formula = y ~ x, method = "lm") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x, method = "lm")
```

### UVA1:PAR photon ratio

```{r}
ggplot(all_data.tb, aes(Q_UVA1.CIE / Q_PAR.McCree, F1 / VIS)) +
  geom_point() +
  stat_poly_line(formula = y ~ x, method = "lm") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x, method = "lm")
```

### Blue

```{r}
ggplot(all_data.tb, aes(Q_Blue.Sellaro * 1e6, F2)) +
  geom_point() +
  stat_poly_line(formula = y ~ x + 0, method = "sma") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x + 0, method = "sma")
```

### Green

```{r}
ggplot(all_data.tb, aes(Q_Green.Sellaro * 1e6, F5)) +
  geom_point() +
  stat_poly_line(formula = y ~ x + 0, method = "sma") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x + 0, method = "sma")
```

### B:G photon ratio

```{r}
ggplot(all_data.tb, aes(Q_Blue.Sellaro / Q_Green.Sellaro, F2 / F5)) +
  geom_point() +
  stat_poly_line(formula = y ~ x, method = "lm") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x, method = "lm")
```

### Red

```{r}
ggplot(all_data.tb, aes(Q_Red.Sellaro * 1e6, F6)) +
  geom_point() +
  stat_poly_line(formula = y ~ x + 0, method = "sma") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x + 0, method = "sma")
```

```{r}
ggplot(all_data.tb, aes(Q_Red.Smith20 * 1e6, F6)) +
  geom_point() +
  stat_poly_line(formula = y ~ x + 0, method = "sma") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x + 0, method = "sma")
```

### Far Red

```{r}
ggplot(all_data.tb, aes(Q_FarRed.Sellaro * 1e6, F8)) +
  geom_point() +
  stat_poly_line(formula = y ~ x - 1, method = "sma") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x - 1, method = "sma")
```

```{r}
ggplot(all_data.tb, aes(Q_FarRed.Smith20 * 1e6, F8)) +
  geom_point() +
  stat_poly_line(formula = y ~ x + 0, method = "sma") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x + 0, method = "sma")
```

### R:FR photon ratio

```{r}
ggplot(all_data.tb, aes(Q_Red.Sellaro / Q_FarRed.Sellaro, F6 / F8)) +
  geom_point() +
  stat_poly_line(formula = y ~ x, method = "lm") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x, method = "lm")
```


```{r}
ggplot(all_data.tb, aes(Q_Red.Smith20 / Q_FarRed.Smith20, F6 / F8)) +
  geom_point() +
  stat_poly_line(formula = y ~ x, method = "lm") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x, method = "lm")
```

Although the estimates of red and far-red irradiances seem good, the estimates of the R:FR photon ratio based on single channels are not as good. While the broader bands of "Sellaro" seem to provide some information those based on "Smith20" are of not use.
This raises the question of how different are the R:FR ratios computed using these two different definitions. As the figure below shows they are far from equivalent in sunlight!

```{r}
ggplot(all_data.tb, aes(Q_Red.Sellaro / Q_FarRed.Sellaro, 
                        Q_Red.Smith20 / Q_FarRed.Smith20)) +
  geom_point() +
  stat_poly_line(formula = y ~ x, method = "lm") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x, method = "lm")
```

The range of meaningful values for R:FR in sunlight is narrow and consequently small errors in the quantification of R and/or FR irradiance result in R:FR errors that can be thought as important for plant responses. Possibly, more important, is that the R:FR photon ratio measured based on different waveband definitions is not consistent in sunlight.

The choice of wavebands is rather arbitrary as the Pfr:Ptot fraction depends on a broad range of wavelengths and different wavelengths affect it with different weights.

### Pfr:Ptot

```{r}
spct.names <- names(test.mspct)
PfrPtot <- numeric()
idx <- 0
for (name in spct.names) {
  idx <- idx + 1L
#  print(name)
  PfrPtot[idx] <- Pfr_Ptot(test.mspct[[name]][ , 1:2])
}
all_data.tb[["Pfr.Ptot"]] <- PfrPtot
```


```{r}
ggplot(all_data.tb, aes(Pfr.Ptot, 
                        Q_Red.Smith20 / Q_FarRed.Smith20)) +
  geom_point() +
  stat_poly_line(formula = y ~ x, method = "lm") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x, method = "lm")
```

```{r}
ggplot(all_data.tb, aes(Pfr.Ptot,
                        Q_Red.Sellaro / Q_FarRed.Sellaro)) +
  geom_point() +
  stat_poly_line(formula = y ~ x, method = "lm") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x, method = "lm")
```

The R:FR ratio based on "Sellaro" definitions describes much better the expected relationship between sunlight and the **expected** _in vitro_ photoequilibrium of phytochrome under sunlight. As seen below, similarly to the R:FR ratio computed using this defintion, the **expected** _in vitro_ photoequilibrium of phytochrome results in a possibly useful relationship to two channels in the AS7343.

```{r}
ggplot(all_data.tb, aes(PfrPtot, F6 / F8)) +
  geom_point() +
  stat_poly_line(formula = y ~ x, method = "lm") +
  stat_poly_eq(use_label("eq", "R2", "n", "AIC"),
               formula = y ~ x, method = "lm")
```
